### 2023-01-23 manuscript.Rmd
Make `read_log` code and comments clearer

      # Behavioral responses
      # Button code 201: "I know what this is or have a strong assumption"
      # Button code 202: "I have an assumption what this is"
      # Button code 203: "I have rather no assumption what this is"
      # Button code 204: "I don't know what this is and have no assumption"
      # Button code 0: Technical glitch
      response = recode(
        Tastencode,
        `201` = 4, `202` = 3, `203` = 2, `204` = 1, `0` = NA_real_
      ),

@@

      # Informed condition: Matching keywords and positive response
      Informed = item_id[
        phase == "Insight" & keywords == "Match" & response %in% c(3, 4)
      ],

      # Naive condition: Non-matching keywords and negative response
      Naive = item_id[
        phase == "Insight" & keywords == "Non-match" & response %in% c(1, 2)
      ],

      # Exclude: Matching keywords and negative response
      Exclude_informed = item_id[
        phase == "Insight" & keywords == "Match" & response %in% c(1, 2)
      ],

      # Exclude: Non-matching keywords and positive response
      Exclude_naive = item_id[
        phase == "Insight" & keywords == "Non-match" & response %in% c(3, 4)
      ],

      # Exclude: Positive response *before* any info was presented
      Exclude_known = item_id[phase == "Pre-insight" & response == 4],

      # Exclude: Technical glitch
      Exclude_glitch = item_id[phase == "Insight" & is.na(response)]
    )
  })

>>>>

      # Behavioral responses
      # Response code 201: "I know what this is or have a strong assumption"
      # Response code 202: "I have an assumption what this is"
      # Response code 203: "I have rather no assumption what this is"
      # Response code 204: "I don't know what this is and have no assumption"
      # Response code 0: Technical glitch
      response = Tastencode,

@@

      # Informed condition: Matching keywords and positive response
      Informed = item_id[
        phase == "Insight" & keywords == "Match" & response %in% c(201, 202)
      ],

      # Naive condition: Non-matching keywords and negative response
      Naive = item_id[
        phase == "Insight" & keywords == "Non-match" & response %in% c(203, 204)
      ],

      # Exclude: Matching keywords and negative response
      Exclude_informed = item_id[
        phase == "Insight" & keywords == "Match" & response %in% c(203, 204)
      ],

      # Exclude: Non-matching keywords and positive response
      Exclude_naive = item_id[
        phase == "Insight" & keywords == "Non-match" & response %in% c(201, 202)
      ],

      # Exclude: Positive response *before* any info was presented
      Exclude_known = item_id[phase == "Pre-insight" & response == 201],

      # Exclude: Technical glitch
      Exclude_glitch = item_id[phase == "Insight" & response == 0]
    )
  })
